\begin{thebibliography}{99}

%Introduction
\bibitem{intro:nupauli} W. Pauli, "Dear radioactive ladies and gentlemen", Phys. Today 31N9, 27 (1978).
\bibitem{intro:reinescowan} F. Reines, C. L. Cowan et al., "Detection of the Free Antineutrino", Phys. Rev. 117, 159 (1960)
\bibitem{intro:lederman} G. Danby et al., "Observation of High-Energy Neutrino Reactions and the Existence of Two Kinds of Neutrinos", Phys. Rev. Lett. 9, 36 (1962)
\bibitem{intro:nu3gen} D. Decamp et al.(ALEPH Collaboration), "Determination of the Number of Light Neutrino Species.", Phys. Lett. B 231, 519–529 (1989).
\bibitem{intro:taunu} K. Kodama et al.(DONUT Collaboration), "Observation of Tau Neutrino Interactions", Phys. Lett.
B, 504(3), 218-224 (2001).
\bibitem{intro:mns} Z. Maki, M. Nakagawa, and S. Sakata, "Remarks on the Unified Model of Elementary Particles", Prog. Theor. Phys. 28, 870-880 (1962)
\bibitem{intro:SKneuosi} Y. Fukuda et al.(Super-Kamiokande Collaboration), "Evidence for Oscillation of Atmospheric Neutrinos", Phys. Rev. Lett. 81, 1562 (1998).
\bibitem{intro:MSWwolfenstein} L. Wolfenstein, "Neutrino Oscillations in Matter", Phys. Rev. D 17, 2369–2374 (1978).
\bibitem{intro:MSWsmirnov} S. P. Mikheyev and A. Yu. Smirnov, "Resonance Amplification of Oscillations in Matter and Spectroscopy of Solar Neutrinos", Sov. J. Nucl. Phys. 42, 913–917 (1985).
\bibitem{intro:Homestake} R. Davis, Jr., D. S. Harmer, and K. C. Hoffman, "Search for Neutrinos from the Sun", Phys. Rev. Lett. 20, 1205–1209 (1968).
\bibitem{intro:kamiokande} K. S. Hirata et al., "Observation of $^8$B Solar Neutrinos in the Kamiokande-II Detector", Phys. Rev. Lett. 63, 16 (1989).
\bibitem{intro:SAGE}  A. I. Abazov et al., "Search for Neutrinos from the Sun Using the Reaction $^{71}$Ga($\nu_e,e^{-}$)$^{71}$Ge", Phys. Rev. Lett. 67, 3332–3335 (1991).
\bibitem{intro:GALLEX} P. Anselmann et al. (GALLEX Collaboration), "Solar Neutrinos Observed by GALLEX at Gran Sasso", Phys. Lett. B 285, 376–389 (1992).
\bibitem{intro:SNO} Q. R. Ahmad et al. (SNO Collaboration), "Direct Evidence for Neutrino Flavor Transformation from Neutral-Current Interactions in the Sudbury Neutrino Observatory", Phys. Rev. Lett. 89, 011301 (2002).
\bibitem{intro:oscipara} F. Capozzi et al., "Unfinished Fabric of the Three Neutrino Paradigm", Phys. Rev. D 104, 083031 (2021).
\bibitem{intro:t2k2023} K.Abe et al. (T2K Collaboration), "Measurements of Neutrino Oscillation Parameters from the T2K Experiment using $3.6\times10^{21}$ protons on target", Eur. Phys. J. C 83, 782 (2023).
\bibitem{intro:sakhanov} A.D. Sakharov, "Violation of CP Invariance, C Asymmetry, and Baryon Asymmetry of the Universe",
Pisma Zh. Eksp. Teor. Fiz. 5, 32-35 (1967).
\bibitem{intro:octant} ZZ. Xing, ZH. Zhao, "A Review of $\mu-\tau$ Flavor Symmetry in Neutrino Physics", Rep Prog Phys. 79(7), 076201 (2016).

\bibitem{t2k:t2k} K. Abe et al.(T2K Collaboration), "The T2K Experiment", Nucl. Instrum. Meth. A 659, 1 (2011).
\bibitem{t2k:t2kgainenzu} https://t2k-experiment.org/ja/about-t2k/
\bibitem{t2k:jparcacc} https://j-parc.jp/Acc/ja/index.html
\bibitem{t2k:offaxis} K. Abe et al.(T2K Collaboration), "Evidence of electron neutrino appearance in a muon neutrino
beam", Phys. Rev. D 88, 032002 (2013).
\bibitem{t2k:mumon} K.Matsuoka et al., "Design and Performance of the Muon Monitor for the T2K Neutrino Oscillation Experiment", Nucl. Instrum. Meth. A 624, 591-600 (2010).

\end{thebibliography}
